Automated Residual Plot Assessment with the R Package autovi and the Shiny App autovi.web

### 2024-11-26 autovi_paper.qmd
Making this more concise.

In the R environment, `autovi` utilizes several libraries. `ggplot2` [@ggplot2] generates the initial residual plots, saved as PNG files for visual input. The `cassowaryr` [@mason2022cassowaryr] library computes scagnostics (scatter plot diagnostics), providing numerical features that capture statistical properties of the plots. These scagnostics complement the visual analysis by offering quantitative metrics as secondary input to the computer vision model. The `reticulate` [@reticulate] package bridges R and Python, enabling seamless communication between the two languages and supporting the integrated infrastructure.

>>>>

In the R environment, `autovi` utilizes several libraries. `ggplot2` [@ggplot2] generates the initial residual plots, saved as PNG files for visual input. `cassowaryr` [@mason2022cassowaryr] computes scagnostics (scatter plot diagnostics), providing numerical features that capture statistical properties of the plots. These scagnostics complement the visual analysis by offering quantitative metrics as secondary input to the computer vision model. `reticulate` [@reticulate]  enables seamless communication between R and Python.
